Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-22 Grassmannian_cells.tex
Section 3.2 edits

@@

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\tbfh}{{\tilde\bfh}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\ui}{\underline i}
\newcommand{\uj}{\underline j}
\newcommand\udim{{\underline{\dim}\, }}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Ind}{\mathrm{Ind}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\rk}{\mathrm{rk}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\setcounter{MaxMatrixCols}{20}
\newcommand{\vs}{\vspace{0.2cm}}
\hyphenation{endo-functors}

@@

Fix a natural number $n\geq 3$ and write $W_n:=W_{K(n)}$ for the free group generated by the arrows $\alpha_i$, $1\le i\le n$, of $K(n)$.
In this section, we fix compatible bases for each $H_m:=\Hom(P_m,P_{m+1})$ and use these to lift the (truncated) preprojectives to the universal cover $\widetilde{K(n)}$ of the quiver $K(n)$.
This lifting will rigidify the situation, allowing more precise control over these representations and their subrepresentation structure.
The main advantage of this lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering quiver $\widetilde{K(n)}$.

We will mainly be interested in particular lifts $\tilde P_m$ of the preprojective representations $P_m$ of $K(n)$ to the universal cover $\widetilde{K(n)}$.
First, recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying the iterated reflection $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
Moreover, under this operation all sinks become sources and vice versa.
The preprojective lifts we use are defined recursively as follows.
\begin{itemize}
  \item For $m=1$, we consider the lift $\tilde P_1$ satisfying $\dim(\tilde P_1)_{(1,1)}=1$ and $\dim (\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,1)$.
  \item For $m=2$, we consider the lift $\tilde P_2$ satisfying $\dim (\tilde P_2)_{(2,1)}=\dim (\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\dim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,1),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
  \item For $m\geq 3$, we build the lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates.
    More precisely, we set
    \begin{align}
      \label{eq:recursive covers}
      \tilde P_m:=(\tilde\Sigma_2 \tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.
    \end{align}
\end{itemize}

It will be rather important that our chosen lifts $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e. $w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation $\tilde P_m$ by the action of $w\in W_n$.
To simplify the notation, we abbreviate $\tilde P_{2l-1,i}:=\tilde P_{2l-1,\alpha_i}$ and $\tilde P_{2l,i}:=\tilde P_{2l,\alpha_i^{-1}}$.
\begin{lemma}
  For each $m\ge2$, the representation $\tilde P_m$ has precisely $n$ subrepresentations covering $P_{m-1}$.
  These are the representations $\tilde P_{m-1,i}$ corresponding to the $n$ different arrows of $K(n)$. 
\end{lemma}
\begin{proof}
  This is clear for $m=2$ and follows in general by applying the identities \eqref{eq:recursive covers}.
\end{proof}
\begin{remark}
  Note that the dimension vectors of the lifted preprojectives $\tilde P_m$ are symmetric.
  In particular, they all have the same middle vertex $(1,1)$ if $m$ is odd and middle vertex $(2,1)$ if $m$ is even.
\end{remark}

Recall that $n\ge3$ is fixed.
Set
\[I_l:=\{(j_1,\ldots,j_l)\mid j_i\in\{1,\ldots,n\},\,j_i\neq j_k\text{ if }i\neq k\}.\]
With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$. More detailed, we obtain a sequence of preprojective representations 
$$\tilde P_{m-k,\ui}\subset \tilde P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-2,(i_1,i_2)}\subset \tilde P_{m-1,i_1}\subset\tilde P_{m}.$$

\begin{lemma}
  \label{le:homdecomposition}
  \sayT{I split up some lemmas. Check references}
  Let $m\geq 2$. The following holds:
  \begin{enumerate}
    \item We have $\Hom_{K(n)}(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\widetilde{K(n)}}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\widetilde{K(n)}}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional.
    \item For $m\geq 1$, the representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e. for $i\neq k$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,k})=0=\Ext(\tilde P_{m,i},\tilde P_{m,k}).\]
    \item For every $\uj\in I_l$, there exists a truncated preprojective representation $\tilde P_{m}^{\uj}$ which is the cokernel of
      \begin{align}
        \label{ses1}
        \ses{\bigoplus_{i=1}^l \tilde P_{m-1,j_i}}{\tilde P_m}{\tilde P_{m}^{\uj}}.
      \end{align}
  \end{enumerate}
\end{lemma}
\begin{proof}
  The first part is immediate from Theorem~\ref{covering}.
  The second part is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq k\leq n$, we have 
  $$\CC=\Hom_Q(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k}).$$
  But $\Hom_{\tilde Q}(\tilde P_{m,k},\tilde P_{m,k})\cong\CC$ and so we must have $\Hom_{\tilde Q}(\tilde P_{m,i},\tilde P_{m,k})=0$ for $i\neq k$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,k})$ follows in the same manner using that $P_m$ is exceptional.
  Now the observations of Section~\ref{sec:truncated preprojectives} immediately yield the final claim.
\end{proof}
In the following, we make use of this lemma and fix a basis of $\Hom(P_{m-1},P_m)$ which is compatible with this direct sum decomposition.
Note that we can quotient out the lifted preprojectives successively, i.e. we have short exact sequences
\[\ses{ \tilde P_{m-1,j_l}}{\tilde P^{(j_1,\ldots,j_{l-1})}_m}{\tilde P_{m}^{\uj}}.\]
\begin{lemma}
  \label{le:properties}
  \sayD{Parts (2) and (3) should follow directly from Lemma~\ref{le:unique morphisms} and the definition of truncated preprojectives for $K(n)$.} 
  For $m\geq 2$ and $\uj\in I_l$, the following hold:
  \begin{enumerate}
    \item We have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\CC$  for $k\neq j_i$ for $i=1,\ldots,l$. 
    \item We have $\Hom(\tilde P_m,\tilde P_m^{\uj})=\CC$ and $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$. 
    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},-)$ to the short exact sequence (\ref{ses1}) using the results of Lemma \ref{le:homdecomposition}.

@@

\begin{corollary}\label{cor: perpendicular}
For $m\geq 3$ and $\uj\in I_l$, we have $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$.
\end{corollary}
\begin{proof}
If $m\geq 4$, we consider the long exact sequence obtained when applying $\Hom(\tilde P_{m}^{\uj},\underline{\quad})$ to the sequence (\ref{ses3}). Using the identities of Lemma \ref{AR}, the result follows.

@@

Corollary \ref{cor: perpendicular} implies that we have $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$ and thus we get $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$.  This yields $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)\cong\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m,j_l})$ and thus $$\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})\cong  \Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U).$$ This means that the induced map
\[\Ext(\tilde P_{m}^{\uj},U)\to\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\]
is zero. Therefore, the induced exact sequence splits. 
Let $\uj'=(j_1,\ldots,j_{l-1})$. On the other hand, every subrepresentation $U\subset \tilde P_{m-1,j_l}$ such that $\Psi_{m,\uj}^{-1}(U,\tilde P_{m}^{\uj})$ is not empty comes with a commutative diagram
 \[\xymatrix{0\ar[r] &\tilde P_{m-1,j_l}\ar[r] &  \tilde P_{m}^{\uj'}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
  e_U: 0\ar[r]& U\ar[r]\ar[u] & U'\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
which means that the image of $e_U$ in $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})$ does not split. This is because we have $\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj'})=0$ by Lemma \ref{le:unique morphisms}. This yields that the fibre $\Psi_{m,\uj}^{-1}(\tilde P_{m}^{\uj},U)$ is empty.

@@

Again we can apply Corollary \ref{cor: perpendicular} in order to see that $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$ as $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$. 
 Together with $\Ext(\tilde P_{m+1}^{\uj},\tau\tilde P_{m}^{\uj}/W)=0$, this yields the claim.

>>>>

\usepackage[inline]{showlabels}

@@

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\tbfh}{{\tilde\bfh}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\ui}{{\underline i}}
\newcommand{\uj}{{\underline j}}
\newcommand\udim{{\underline{\dim}\, }}
\newcommand{\pt}{\mathrm{pt}}
\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Ind}{\mathrm{Ind}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\rk}{\mathrm{rk}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\setcounter{MaxMatrixCols}{20}
\newcommand{\vs}{\vspace{0.2cm}}
\hyphenation{endo-functors}

@@

Fix a natural number $n\geq 3$ and write $W_n:=W_{K(n)}$ for the free group generated by the arrows $\alpha_i$, $1\le i\le n$, of $K(n)$.
In this section, we fix compatible bases for each $H_m:=\Hom(P_m,P_{m+1})$ and use these to lift the (truncated) preprojective representations of the quiver $K(n)$ to the universal cover~$\widetilde{K(n)}$.
This lifting will rigidify the situation, allowing more precise control over these representations and their subrepresentation structure.
Of particular importance is Corollary~\ref{cor:perpendicular} which has no reasonable analogue for $K(n)$.
One main advantage of the lifting is that those truncated preprojectives which can be lifted are exceptional representations on the universal covering quiver $\widetilde{K(n)}$.

We will mainly be interested in particular lifts $\tilde P_m$ of the preprojective representations $P_m$ of $K(n)$ to the universal cover $\widetilde{K(n)}$.
First, recall that applying the BGP-reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying the iterated reflection $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.
Moreover, under this operation all sinks of~$\widetilde{K(n)}$ become sources and vice versa.
The preprojective lifts we use are defined by the following analogue of the recursions of Remark~\ref{rem:reflection recursion}.
\begin{itemize}
  \item For $m=1$, we consider the lift $\tilde P_1$ satisfying $\dim(\tilde P_1)_{(1,1)}=1$ and $\dim (\tilde P_1)_{(i,w)}=0$ for $(i,w)\neq (1,1)$.
  \item For $m=2$, we consider the lift $\tilde P_2$ satisfying $\dim (\tilde P_2)_{(2,1)}=\dim (\tilde P_2)_{(1,\alpha_i)}=1$ for $1\le i\le n$ and $\dim(\tilde P_2)_{(i,w)}=0$ for $(i,w)\notin\{(2,1),(1,\alpha_1),\ldots,(1,\alpha_n)\}$.
  \item For $m\geq 3$, we build the lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translates.
    More precisely, we set
    \begin{align}
      \label{eq:recursive covers}
      \tilde P_m:=(\tilde\Sigma_2 \tilde P_{m-1})^{\sigma}\qquad\text{or}\qquad\tilde P_{m+1}:=\tilde\Sigma_{1}\tilde\Sigma_2\tilde P_{m-1}=\tau^{-1} \tilde P_{m-1}.
    \end{align}
\end{itemize}

It will be rather important that our chosen lifts $\tilde P_{2l}$ and $\tilde P_{2l-1}$ live on two different components of the universal covering quiver.
Indeed, recall that the group $W_n$ naturally acts on $\widetilde{K(n)}_0$ via translation, i.e.~$w.(i,w')=(i,ww')$, and this induces an action of $W_n$ on $\rep\widetilde{K(n)}$.
Following the notation of Section~\ref{sec:covering}, we write $\tilde P_{m,w}$ for the representation of $\widetilde{K(n)}$ obtained by translating the lifted preprojective representation $\tilde P_m$ by the action of $w\in W_n$.
To simplify the notation, we abbreviate $\tilde P_{2l-1,i}:=\tilde P_{2l-1,\alpha_i}$ and $\tilde P_{2l,i}:=\tilde P_{2l,\alpha_i^{-1}}$.
\begin{lemma}
  For each $m\ge1$, the representation $\tilde P_{m+1}$ has precisely $n$ subrepresentations covering $P_m$.
  These are the representations $\tilde P_{m,i}$ corresponding to the $n$ different arrows of $K(n)$. 
\end{lemma}
\begin{proof}
  This is clear for $m=1$ and follows in general by applying the identities \eqref{eq:recursive covers}.
\end{proof}
\begin{remark}
  Note that the dimension vectors of the lifted preprojectives $\tilde P_m$ are symmetric.
  In particular, they all have the same middle vertex $(1,1)$ if $m$ is odd and middle vertex $(2,1)$ if $m$ is even.
\end{remark}

Now we introduce notation for locating lifted preprojectives as subrepresentations of other lifted preprojective representations.
Set
\[A_1^{(l)}:=\{(i_1,\ldots,i_l)\mid i_j\in\{1,\ldots,n\},\,i_j\neq i_k\text{ if }j\neq k\}.\]
Depending on context (more specifically the parity of $m+1$ below), we will sometimes identify the word $(i_1,\ldots,i_l)$ with the element $\alpha_{i_1}\alpha_{i_2}^{-1}\alpha_{i_3}\cdots\alpha_{i_l}^{(-1)^{l+1}}\in W_n$ and sometimes with the element $\alpha_{i_1}^{-1}\alpha_{i_2}\alpha_{i_3}^{-1}\cdots\alpha_{i_l}^{(-1)^l}\in W_n$.
In this way, we associate to each $\ui=(i_1,\ldots,i_k)\in A_1^{(k)}$, $1\leq k\leq m$, a preprojective subrepresentation $\tilde P_{m+1-k,\ui}\subset\tilde P_{m+1}$ which lifts $P_{m+1-k}$.
More precisely, we obtain a sequence of preprojective representations 
\[\tilde P_{m+1-k,\ui}\subset \tilde P_{m+2-k,(i_1,\ldots,i_{k-1})}\subset\ldots\subset \tilde P_{m-1,(i_1,i_2)}\subset \tilde P_{m,i_1}\subset\tilde P_{m+1}.\]
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom_{K(n)}(P_m,P_{m+1})\cong\bigoplus_{i=1}^n \Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For every $\ui\in A_1^{(l)}$, there exists a truncated preprojective representation $\tilde P_{m+1}^\ui$ which is the cokernel of
      \begin{align}
        \label{ses1}
        \ses{\bigoplus_{j=1}^l \tilde P_{m,i_j}}{\tilde P_{m+1}}{\tilde P_{m+1}^{\ui}}.
      \end{align}
  \end{enumerate}
\end{lemma}
\begin{proof}
  The first part is immediate from Theorem~\ref{covering}.
  The second part is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq k\leq n$, we have 
  $$\CC=\Hom_{K(n)}(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom_{\widetilde{K(n)}}(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom_{\widetilde{K(n)}}(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

  For the final claim, observe that under the isomorphism from part (1) the sequence $\ui\in A_1^{(l)}$ corresponds to an $l$-dimensional subspace $V\in H_m$.
  The map $\bigoplus_{j=1}^l \tilde P_{m,i_j}\to \tilde P_{m+1}$ is then a lift of the evaluation morphism $ev_V:P_m\otimes V\to P_{m+1}$ and hence is injective by Lemma~\ref{le:injective evaluation maps}.
  Taking the cokernel defines the truncated preprojective $\tilde P_{m+1}^\ui$.
\end{proof}
In the following, we make use of this lemma and fix a basis of $\Hom(P_{m-1},P_m)$ which is compatible with this direct sum decomposition.
Note that we can quotient out the lifted preprojectives successively, i.e. we have short exact sequences
\[\ses{ \tilde P_{m-1,j_l}}{\tilde P^{(j_1,\ldots,j_{l-1})}_m}{\tilde P_{m}^{\uj}}.\]
\begin{lemma}
  \label{le:properties}
  \sayD{Parts (2) and (3) should follow directly from Lemma~\ref{le:unique morphisms} and the definition of truncated preprojectives for $K(n)$.} 
  For $m\geq 2$ and $\uj\in I_l$, the following hold:
  \begin{enumerate}
    \item We have $\Hom(\tilde P_{m-1,k},\tilde P_m)\cong\Hom(\tilde P_{m-1,k},\tilde P_m^{\uj})=\CC$  for $k\neq j_i$ for $i=1,\ldots,l$. 
    \item We have $\Hom(\tilde P_m,\tilde P_m^{\uj})=\CC$ and $\Ext(\tilde P_{m},\tilde P_{m}^{\uj})=0$. 
    \item We have $\Ext(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj})=0$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  The first identity of the last statement follows when applying $\Hom(\tilde P_{m-1,k},-)$ to the short exact sequence (\ref{ses1}) using the results of Lemma \ref{le:homdecomposition}.

@@

\begin{corollary}\label{cor:perpendicular}
For $m\geq 3$ and $\uj\in I_l$, we have $P(m,\uj)\in (\tilde P_{m}^{\uj})^\perp$.
\end{corollary}
\begin{proof}
If $m\geq 4$, we consider the long exact sequence obtained when applying $\Hom(\tilde P_{m}^{\uj},\underline{\quad})$ to the sequence (\ref{ses3}). Using the identities of Lemma \ref{AR}, the result follows.

@@

Corollary \ref{cor:perpendicular} implies that we have $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$ and thus we get $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$.  This yields $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U)\cong\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m,j_l})$ and thus $$\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\cong\Ext(\tilde P_{m}^{\uj},\tau\tilde P_{m}^{\uj})\cong  \Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l}/U).$$ This means that the induced map
\[\Ext(\tilde P_{m}^{\uj},U)\to\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})\]
is zero. Therefore, the induced exact sequence splits. 
Let $\uj'=(j_1,\ldots,j_{l-1})$. On the other hand, every subrepresentation $U\subset \tilde P_{m-1,j_l}$ such that $\Psi_{m,\uj}^{-1}(U,\tilde P_{m}^{\uj})$ is not empty comes with a commutative diagram
 \[\xymatrix{0\ar[r] &\tilde P_{m-1,j_l}\ar[r] &  \tilde P_{m}^{\uj'}\ar[r] & \tilde P_{m}^{\uj}\ar[r] & 0 \\
  e_U: 0\ar[r]& U\ar[r]\ar[u] & U'\ar[u]\ar[r]& \tilde P_{m}^{\uj}\ar[r]\ar@{=}[u]& 0}\]
which means that the image of $e_U$ in $\Ext(\tilde P_{m}^{\uj},\tilde P_{m-1,j_l})$ does not split. This is because we have $\Hom(\tilde P_{m}^{\uj},\tilde P_{m}^{\uj'})=0$ by Lemma \ref{le:unique morphisms}. This yields that the fibre $\Psi_{m,\uj}^{-1}(\tilde P_{m}^{\uj},U)$ is empty.

@@

Again we can apply Corollary \ref{cor:perpendicular} in order to see that $\Ext(\tilde P_{m}^{\uj},P(m,\uj)/V)=0$ as $\Ext(\tilde P_{m}^{\uj},P(m,\uj))=0$. 
 Together with $\Ext(\tilde P_{m+1}^{\uj},\tau\tilde P_{m}^{\uj}/W)=0$, this yields the claim.
